### 2018-08-07 manuscript.rmd
switched to bayesian tree

```{r load_tree, include=F}
#Load tree
consensus = ape::read.tree("concatenate.fasta.contree")
consensus = reroot(consensus,103)
consensus = drop.tip(consensus, c(28,29,30,59:61))
consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")

@@

>>>>

```{r load_tree, include=F}
#Load tree
#consensus = ape::read.tree("concatenate.fasta.contree")
consensus = read.nexus("gene_map_ct.tre")
read.tree("gene_ct.trees") %>% consensus() -> daconsensus
plot(daconsensus)
#consensus = reroot(consensus,103)
consensus = reroot(consensus,97)
#consensus = drop.tip(consensus, c(28,29,30,59:61))
consensus = drop.tip(consensus, c(56:61))
consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
ultra_consensus = chronos(consensus,100)

#PLOT tree figure
plot(ultra_consensus)

@@

```{r simmaps, include=F}
par(ask=F)
tentilla = sharedcategorical$Tentilla
names(tentilla) = rownames(sharedcategorical)
prox_het = sharedcategorical$Proximal.heteronemes
names(prox_het) = rownames(sharedcategorical)
desmo = sharedcategorical$Desmonemes
names(desmo) = rownames(sharedcategorical)
rhopalo = sharedcategorical$Rhopalonemes
names(rhopalo) = rownames(sharedcategorical)
dyn_cnido = sharedcategorical$Dynamic.cnidoband
names(dyn_cnido) = rownames(sharedcategorical)
elastic = sharedcategorical$Elastic.strand
names(elastic) = rownames(sharedcategorical)
distal_desmo = sharedcategorical$Distal.cnidoband.desmonemes
names(distal_desmo) = rownames(sharedcategorical)
coiled = sharedcategorical$Coiled.tentilla
names(coiled) = rownames(sharedcategorical)
heterotype = sharedcategorical$Heteroneme.type
heterotype=as.character(heterotype)
names(heterotype) = rownames(sharedcategorical)
haplotype = sharedcategorical$Haploneme.type
haplotype=as.character(haplotype)
names(haplotype) = rownames(sharedcategorical)

Simmap_list = list()
###SIMMAP Tentilla:
make.simmap(ultram_cat, tentilla, nsim = 100) -> tentilla_sim
Simmap_list[[1]] <- tentilla_sim
plotTree(ultram_cat, lwd = 4)
tentilla_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Present", "Absent")
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)

###SIMMAP Proximal Heteronemes:
make.simmap(ultram_cat, prox_het, nsim = 100) -> prox_het_sim
Simmap_list[[2]] <- prox_het_sim
plotTree(ultram_cat, lwd = 4)
prox_het_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Present", "Absent")
nodelabels(pie=(describe.simmap(prox_het_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(prox_het_sim)

###SIMMAP Desmonemes:
make.simmap(ultram_cat, desmo, nsim = 100) -> desmo_sim
Simmap_list[[3]] <- desmo_sim
plotTree(ultram_cat, lwd = 4)
desmo_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(desmo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(desmo_sim)

###SIMMAP Rhopalonemes:
make.simmap(ultram_cat, rhopalo, nsim = 100) -> rhopalo_sim
Simmap_list[[4]] <- rhopalo_sim
plotTree(ultram_cat, lwd = 4)
rhopalo_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(rhopalo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(rhopalo_sim)

###SIMMAP Dynamic Cnidoband:
make.simmap(ultram_cat, dyn_cnido, nsim = 100) -> dyn_cnido_sim
Simmap_list[[5]] <- dyn_cnido_sim
plotTree(ultram_cat, lwd = 4)
dyn_cnido_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(dyn_cnido_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(dyn_cnido_sim)

###SIMMAP Elastic Strand:
make.simmap(ultram_cat, elastic, nsim = 100) -> elastic_sim
Simmap_list[[6]] <- elastic_sim
plotTree(ultram_cat, lwd = 4)
elastic_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(elastic_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(elastic_sim)

###SIMMAP Distal CB Desmonemes:
make.simmap(ultram_cat, distal_desmo, nsim = 100) -> distal_desmo_sim
Simmap_list[[7]] <- distal_desmo_sim
plotTree(ultram_cat, lwd = 4)
distal_desmo_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(distal_desmo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(distal_desmo_sim)

###SIMMAP Tentilla Coiledness:
make.simmap(ultram_cat, coiled, nsim = 100) -> coiled_sim
Simmap_list[[8]] <- coiled_sim
plotTree(ultram_cat, lwd = 4)
coiled_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(coiled_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(coiled_sim)

###SIMMAP Heteroneme type:
heterotype = heterotype[heterotype!=""]
HTtree = drop.tip(ultram_cat, which(!(ultram_cat$tip.label %in% names(heterotype))))
make.simmap(HTtree, heterotype, nsim = 100) -> heterotype_sim
Simmap_list[[9]] <- heterotype_sim
plotTree(HTtree, lwd = 4)
heterotype_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green")
names(colors) = c("Eurytele", "Microbasic mastigophore", "Stenotele")
nodelabels(pie=(describe.simmap(heterotype_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)

###SIMMAP Haploneme type:
haplotype = haplotype[haplotype!=""]
HTtree = drop.tip(ultram_cat, which(!(ultram_cat$tip.label %in% names(haplotype))))
make.simmap(HTtree, haplotype, nsim = 100) -> haplotype_sim
Simmap_list[[10]] <- haplotype_sim
plotTree(HTtree, lwd = 4)
haplotype_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Isorhizas", "Anisorhizas")
nodelabels(pie=(describe.simmap(haplotype_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(haplotype_sim)
